Viscous Erosion in Porous Media

### 2018-02-27 docs/methods/erosion_methods.tex
NM

In Fig.~\ref{area_drag}(b), we show the drag $F_D$ measured on the body as it erodes. The drag decreases gradually, then takes a nose dive in the final moments when the body vanishes, as is consistent with the logarithmic dependence on lengthscale $L$ in 2D Stokes flow. We also show in the figure the separate contributions of the viscous and the pressure drag. As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
\begin{align}
\label{viscdrag}
F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
\end{align}
This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag. Of course, \eqref{viscdrag} is less accurate than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.

>>>>

In Fig.~\ref{area_drag}(b), we show the drag $F_D$ measured on the body as it erodes. The drag decreases gradually, then takes a nose dive in the final moments when the body vanishes, as is consistent with the logarithmic dependence on lengthscale $L$ in 2D Stokes flow. We also show in the figure the separate contributions of the viscous and the pressure drag. As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
\begin{align}
\label{viscdrag}
F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
\end{align}
This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag. Of course, \eqref{viscdrag} is less exact than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.
